\documentclass[11pt]{article}

\usepackage{a4wide}
\usepackage{mathptm}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{shapes.misc, positioning}
\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=left,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
\begin{document}

\title{Software Technology Evaluation Project}

\maketitle

\begin{abstract}
The software technology stack for our voting application is an integration of React, Tailwind CSS, Spring Boot, JPA with Hibernate, and an H2 database. React's declarative UI paradigm combined with Tailwind CSS's utility-first styling affords a seamless and responsive front-end experience. The Spring Boot framework underpins the back-end, facilitating rapid development and deployment with its embedded server and 'convention over configuration' philosophy. JPA, implemented via Hibernate, abstracts the complexity of database interactions with an ORM layer, promoting a robust data access strategy. The H2 database provides a lightweight, file-based database, perfect for development and testing phases due to its simplicity and speed. The project's highlights include a secure, scalable architecture with a focus on clean, maintainable code and an emphasis on user experience. Authentication is streamlined through Firebase, ensuring secure access and data integrity. The application's design, leveraging containerization with Docker, ensures consistent environments across development, testing, and production. The result is an intuitive voting platform that is both developer-friendly and scalable.
\end{abstract}

%\input{commands}

\input{sections/introduction}

\input{sections/technology}

\input{sections/design}

\input{sections/implementation}

\input{sections/evaluation}

\input{sections/conclusion}

\input{sections/references}

\end{document}
